\label{task1}
\section{Global Requirements}
% 1. Identify the global requirements on the whole system in natural language. A typical requirement is that ‘the patient support system may never make a motorised horizontal movement while in emergency mode’. 

In this section, we formally state the global requirements of the Move-able Patient Support System (MPSP) which have been derived by the problem statement of the assignment. 
\begin{itemize}
    \item \textbf{P01} If a motor is on, the corresponding brake must not be applied. \\
    \item \textbf{P02:} The horizontal motor should be on only if the MPSP is docked. \\ 
    \item \textbf{P03:} The horizontal brake should not be applied if the MPSP is docked. \\ 
    \item \textbf{P04:} The bed must be in the rightmost position if the MPSP is  undocked. \\ 
    \item \textbf{P05:} The horizontal brake must be applied if the MPSP is undocked. \\
    \item \textbf{P06:} The vertical brake must always be applied if the vertical motor is off. \\
    \item \textbf{P07:} The vertical brake must always be applied if the MPSP is docked. \\ 
    \item \textbf{P08:} In emergency mode, the horizontal brake must be released. \\
    \item \textbf{P09:} If the MPSP is undocked and uncalibrated, the bed should only be moved up and down. \\
    \item \textbf{P10:} The MPSP should not move above the uppermost position, below the lowermost position. \\
\end{itemize}

\begin{itemize}
    \item \textbf{P11:}  When the MPSP is docked and at the rightmost position, the \verb$reset$ button will set the standard height. \\
    \item \textbf{P12:} When the MPSP is undocked and the \verb$reset$ button is pressed, the standard height is forgotten.\\
    \item \textbf{P13:} If the MPSP is docked and calibrated, the vertical brakes are applied and the vertical motor turned off. \\
    \item \textbf{P14:} If the \verb$stop$ button is pressed, the MPSP goes into emergency mode. \\
    \item \textbf{P15:} When the MPSP goes into emergency mode, the horizontal brake is released so that the patient can be taken out of the scanner. \\
    \item \textbf{P16:} When the MPSP is in emergency mode, the \verb$resume$ button puts it back into the normal functioning mode.  \\
    \item \textbf{P17:} When the MPSP is docked and in the rightmost position, \verb$undock$ button sends a message to the scanner to disconnect.\\
    \item \textbf{P18:}  When the MPSP is docked and not at the rightmost position, the \verb$down$ button moves the bed to the left (towards the out of the scanner). \\
    \item \textbf{P19:} When the MPSP is docked and calibrated, the \verb $up$ button moves the bed into the scanner. \\
    \item \textbf{P20:} When the MPSP is docked, uncalibrated and lower than the uppermost position, the \verb$up$ button moves the bed upwards. \\
    \item \textbf{P21:} When the MPSP is docked, uncalibrated and above the lowermost position, the \verb$down$ button moves the bed downwards. \\

     
\end{itemize}